An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-01-13 preprint/manuscript.tex
minor tweaks

We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions are shown in Figure~\ref{fig:sampling}.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance. We chose to exclude these cases to be conservative.}\label{fig:sampling}
\end{figure*}

@@

Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as Registered Reports we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

The main dependent variable was whether or not the first hypothesis was supported or not, as reported by the authors.
We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:

@@

Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
Coding disagreements between full and partial support were deemed minor since they would not affect the final results, thus only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.

@@

Based on our experiences during the pilot, we added one coding criterion:
If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first tested hypothesis rather than the first hypothesis mentioned in the text.
In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs \(= 33.80\%\) and \(47\) SRs \(= 30.92 \%\)).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(21.05 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
All of these are documented in the Appendix and our shared dataset and codebook.

@@

\begin{quote}
A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports in psychology.
In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of \(5\%\) (Lakens, Scheel, \& Isager, 2018).
We determined our smallest effect size of interest to be the difference between the positive result rate in psychology (\(91.5\%\)) and the positive result rate in general social sciences (\(85.5\%\)) as reported by Fanelli (2010), i.e.~a difference of \(91.5\% - 85.5\% = 6\%\).
The rationale for choosing general social sciences as a comparison is that this discipline had the lowest positive result rate amongst the \enquote{soft} sciences (Fanelli, 2010).
The exact percentage for general social sciences was extracted from Figure 1 in Fanelli (2010) using the software WebPlotDigitizer (Rohatgi, 2018).
\end{quote}

@@

As described in the Method section, we only classified close or direct replications of previously published work as replications.
This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 Registered Reports (\(57.75\%\)), but only 4 out of 152 standard reports (\(2.63\%\)) were classified as direct replications of previously published work.
However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports -- \(45.95\%\) -- was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Since our standard reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\). This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = -3.73\), \(p= .306\)), both at \(\alpha = 5\%\).
In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
The data are inconclusive.

Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captured the way researchers write about hypothesis tests reasonably well. The answer is a resounding \enquote{no}:
Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only 2/71 Registered Reports would have been detected with this search phrase.
To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.

For the majority of Registered Reports (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
In order to condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word. Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, while only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports did.

We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis. As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.
Tables 2 and 3 list all unique hypothesis introductions and their frequency for original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.

@@

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
We searched their titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.

@@

Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to.
Standard publication formats seem to lead scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature.
The absence of negative results is a serious threat to a cumulative science.
Reliable protection against questionable research practices and publication bias is crucial to ensure the integrity of the literature.
The Registered Reports format is a promising candidate for bias protection, but we are only at the beginning of understanding its effectiveness and robustness in different contexts and scientific disciplines.

>>>>

We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the Registered Reports population.
We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions is shown in Figure~\ref{fig:sampling}.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: four of these had been treated as Registered Reports but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance (we chose to exclude these cases to be conservative).}\label{fig:sampling}
\end{figure*}

@@

Following these exclusions, we verified the Registered Reports status of all remaining papers in our sample.
Papers were counted as Registered Reports if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as Registered Reports, we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS Registered Reports database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly Registered Reports, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 Registered Reports for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

The main dependent variable was whether the first hypothesis was supported or not, as reported by the authors.
We tried to follow Fanelli's (2010) coding procedure as closely as possible, which he describes as follows:

@@

Like Fanelli (2010), we coded hypotheses as having received \enquote{support}, \enquote{partial support}, or \enquote{no support}, which was recoded into a binary \enquote{support} (full or partial) vs \enquote{no support} variable for the analysis.
Coding disagreements between full and partial support were deemed minor since they would not affect the final results. Thus, only disagreements affecting the binary support/no support classification were treated as major and resolved through discussion.

@@

Based on our experiences during the pilot, we added one coding criterion:
If the first hypothesis mentioned in a paper was not explicitly tested but subsequently divided into sub-hypotheses that were tested, we would code the first \emph{tested} hypothesis rather than the first hypothesis mentioned in the text.
In Registered Reports we coded the first preregistered hypothesis, thus excluding unregistered pilot studies.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We had preregistered that AS would additionally code a random subset of both groups, but decided against it because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria had led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for papers that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

All additional measures we collected but have not described thus far were either auxiliary variables to facilitate the coding process or earlier versions of the variables discussed above.
All of these are documented in the Appendix and in our shared dataset and codebook.

@@

\begin{quote}
A one-sided proportion test with an alpha level of \(5\%\) will be performed to test whether the positive result rate (full or partial support) of Registered Reports in psychology is statistically lower than the positive result rate of conventional reports {[}we later changed the term to \enquote{standard reports}{]} in psychology.
In addition to testing if there is a statistically significant difference between RRs and conventional reports, we will test if the difference is smaller than our smallest effect size of interest using an equivalence test for proportion tests with an alpha level of \(5\%\) (Lakens, Scheel, \& Isager, 2018).
We determined our smallest effect size of interest to be the difference between the positive result rate in psychology (\(91.5\%\)) and the positive result rate in general social sciences (\(85.5\%\)) as reported by Fanelli (2010), i.e.~a difference of \(91.5\% - 85.5\% = 6\%\).
The rationale for choosing general social sciences as a comparison is that this discipline had the lowest positive result rate amongst the \enquote{soft} sciences (Fanelli, 2010).
The exact percentage for general social sciences was extracted from Figure 1 in Fanelli (2010) using the software WebPlotDigitizer (Rohatgi, 2018).
\end{quote}

@@

As described in the Method section, we only classified close or direct replications of previously published work as replications.
This means that our non-replication category also contains some conceptual replications and \enquote{internal} replications (where original and replication are published in the same paper).
For ease of communication we will nonetheless refer to this category as \enquote{original} studies.
As expected, direct replications were much more common among Registered Reports than standard reports: 41 out of 71 Registered Reports (\(57.75\%\)), but only 4 out of 152 standard reports (\(2.63\%\)) were classified as direct replications of previously published work.
However, this difference cannot account for the stark overall difference between standard reports and Registered Reports described above:
Although replication Registered Reports in our sample indeed had a lower positive result rate than original Registered Reports (see Table 1), the difference between original standard reports and original Registered Reports, \(45.95\%\), was still significantly different from 0 (\(\chi^2 = 46.28\), \(p < .001\)) and not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = 4.31\), \(p > .999\)), both at \(\alpha = 5\%\).

@@

Since our standard-reports sample represents a direct replication of Fanelli (2010) for the discipline Psychiatry \& Psychology, another interesting question to ask is how our results compare to Fanelli's.
The difference between the positive result rate for standard reports in our sample (\(96.05\%\)) and Fanelli's (\(91.49\%\)) is \(4.56\%\). This difference is not significantly different from 0 in a two-sided proportions test (\(\chi^2 = 1.91\), \(p= .167\)) but also not statistically equivalent to a range between \(-6\%\) and \(6\%\) (\(z = -3.73\), \(p= .306\)), both at \(\alpha = 5\%\).
In other words, we can neither reject the hypothesis that the positive result rates of the two populations are the same, nor that there is a difference of at least \(\pm 6\%\) between them.
The data are inconclusive.

Finally, we analysed the language that was used to introduce or refer to hypotheses in Registered Reports.
We were interested in whether the search phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} used by Fanelli captures the way researchers write about hypothesis tests reasonably well. The answer is a resounding \enquote{no}:
Searching the abstracts, titles, and keywords of the Registered Reports sample showed that only 2/71 Registered Reports would have been detected with this search phrase.
To get an overview of analogous hypothesis-introduction phrases researchers used in Registered Reports, we stripped the hypothesis quotes of Registered Reports from all content-specific information and extracted \enquote{minimal} phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote \enquote{(f)or Study 1, we predicted that participants reading about academic (vs.~social) behaviors would show a better anagram performance} we extracted the hypothesis-introduction phrase \enquote{predicted that}.

For the majority of Registered Reports (49), we identified one hypothesis-introduction phrase; the remaining ones used two (16 RRs), three (4 RRs), or four (1 RR) different phrases or had no identifiable hypothesis introduction (1 RR).
In this total set of 97 hypothesis introductions, we found 64 unique phrases, showing substantial linguistic variation (see Tables 2 and 3).
In order to condense the information, we listed all unique word stems (e.g., the word stem \enquote{hypothes\(^\ast\)} captures the words \enquote{hypothesis}, \enquote{hypotheses}, \enquote{hypothesize}, \enquote{hypothesized}, and so on) and analysed their frequency among all hypothesis introductions.
Excluding words that are common but too unspecific by themselves, such as \enquote{that}, \enquote{to}, or \enquote{whether}, the five most frequent word stems were \enquote{hypothes\(^\ast\)} (34 occurrences), \enquote{replicat\(^\ast\)} (24), \enquote{test\(^\ast\)} (20), \enquote{examine\(^\ast\)} (8), and \enquote{predict\(^\ast\)} (8).
Clearly \enquote{test\(^\ast\)} and \enquote{hypothes\(^\ast\)} are quite popular, yet they co-occurred only 8 times and more than half of all hypothesis introductions (51/97) contained neither word. Interestingly, the frequency of these two words differed between original studies and direct replications: 30 out of 43 (\(69.77\%\)) hypothesis introductions found in original Registered Reports contained either \enquote{test\(^\ast\)} or \enquote{hypothes\(^\ast\)} or both, but the same was true for only 16 out of 54 (\(29.63\%\)) hypothesis introductions in direct replication Registered Reports.

We noticed that direct replication Registered Reports generally tended to use different language to describe their hypothesis. As the high frequency of the word stem \enquote{replicat\(^\ast\)} suggests, these studies were often not framed as new tests of a previously tested hypothesis, but as attempts to replicate a previously documented effect or to repeat a previously conducted experiment.
Authors thus seemed to have focussed more on the goal to replicate a previous finding than to test a hypothesis.

Tables 2 and 3 list all unique hypothesis introductions and their frequency in original Registered Reports and direct replication Registered Reports, respectively, grouped by the five most frequent word stems (\enquote{hypothes\(^\ast\)}, \enquote{replicat\(^\ast\)}, \enquote{test\(^\ast\)}, \enquote{examine\(^\ast\)}, \enquote{predict\(^\ast\)}).
Using five as a cut-off value is an arbitrary decision, but we believe that it strikes a reasonable balance between condensing the information and doing the variance of the data justice.

@@

It is important to keep in mind that not all hypotheses could be coded from the abstract: For 21 Registered Reports, the hypothesis introduction phrases analysed above came only from the full text, which means that search terms extracted from them may not be useful in literature searches focussed only on titles, abstracts, and keywords.
Therefore we additionally tested how many of the Registered Reports would have been detected in a regular search using our five most frequent word stems.
We searched titles, abstracts, and keywords for \enquote{hypothes\(^\ast\)} OR \enquote{replicat\(^\ast\)} OR \enquote{test\(^\ast\)} OR \enquote{examine\(^\ast\)} OR \enquote{predict\(^\ast\)} and found that \(69/71\) Registered Reports (\(97.18 \%\)) would have been detected this way.
We do not know how well these search terms represent the population of hypothesis-testing studies in Psychology, but a structured investigation of this question would be very useful for future meta-research.

@@

Our study presents a systematic comparison of positive results in Registered Reports and the standard literature. The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the published research we are used to. Standard publication formats seem to lead psychological scientists to miss out on many high-quality studies with negative results, which are available in the Registered Reports literature. The absence of negative results is a serious threat to a cumulative science. In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left. In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature -- and may be one solution to a much more credible record of the research scientists conduct.
